An antibody-escape calculator for mutations to the SARS-CoV-2 receptor-binding domain

### 2021-12-02 paper/paper.tex
draft of intro

\lettrine[lines=2]{\color{color2}T}{}he last two years...

@@

\section{Acknowledgments}
{\color{red} More}
JDB is an Investigator of the Howard Hughes Medical Institute.

>>>>

\lettrine[lines=2]{\color{color2}H}{}uman coronaviruses undergo rapid antigenic evolution that erodes antibody-based neutralization~\citep{eguia2021human,kistler2021evidence}.
This antigenic evolution is already apparent for SARS-CoV-2, as a variety of new viral variants with reduced antibody neutralization have already emerged only $\sim$2 years since the virus first started to spread in humans~\citep{?}.
A tremendous amount of experimental effort has been expended to characterize these SARS-CoV-2 variants in neutralization assays~\citep{?}.
Unfortunately, the rate at which new variants arise and spread can outstrip the speed with which these laborious experiments can be performed.

A partial solution is to use deep mutational scanning experiments to \emph{prospectively} characterize how viral mutations impact antibody binding or neutralization.
These experiments can systematically map the antigenic impacts of all possible amino-acid mutations in key regions of spike on specific antibodies or serum samples~\citep{?}.
However, SARS-CoV-2 variants of concern typically have many mutations in spike, and it is not feasible to experimentally characterize all combinations of mutations even via high-throughput approaches such as deep mutational scanning.

Here we provide a partial solution to this challenge by aggregating deep mutational scanning data across many antibodies to assess the impacts of combinations of mutations in the spike receptor-binding domain (RBD), which is the primary target of neutralizing antibodies to SARS-CoV-2~\citep{?}.
The resulting ``escape calculator'' enables both qualitative visualization and quantitative scoring of the antigenic impacts of arbitrary combinations of RBD mutations.

@@

\section{Acknowledgments}
{\color{red} GISAID}
JDB is an Investigator of the Howard Hughes Medical Institute.
